Analysis

### 2022-05-17 EDA_PWMScan.Rmd
Playing with GenometriCorr

```{r libraries}
library(tidyverse)
library(readxl)
library(writexl)
library(rtracklayer)
library(stringr)
library(cowplot)
library(stringr)
library("ggsci")
library(scales)
# scales::show_col(pal_lancet("lanonc")(8))
mycols = pal_lancet("lanonc")(8)
library(plyranges)
library(patchwork)
```

@@

>>>>

```{r libraries}
library(tidyverse)
library(readxl)
library(writexl)
library(rtracklayer)
library(stringr)
library(cowplot)
library(stringr)
library("ggsci")
library(scales)
# scales::show_col(pal_lancet("lanonc")(8))
mycols = pal_lancet("lanonc")(8)
library(plyranges)
library(pheatmap)
library(patchwork)
library(GenometriCorr)
```

@@

## Jaccard

```{r jaccard, warning=FALSE, fig.width=6.5, fig.height=6}
save_pheatmap_svg <- function(x, filename, width=4.5, height=3, units = "in", res = 300) {
  stopifnot(!missing(x))
  stopifnot(!missing(filename))
  svg(filename, width=width, height=height)
  grid::grid.newpage()
  grid::grid.draw(x$gtable)
  dev.off()
}
# Jaccard calculations
jaccard <- function(gr_a, gr_b) {
  intersects <- GenomicRanges::intersect(gr_a, gr_b, ignore.strand = TRUE)
  intersection <- sum(width(intersects))
  union <- sum(width(GenomicRanges::union(gr_a, gr_b, ignore.strand = TRUE)))
  DataFrame(intersection, union, 
            jaccard = intersection/union,
             n_intersections = length(intersects))
}
# Correlation matrix, empty
mtx_to_plot <- matrix(data = 0, nrow = length(bed_list_standard), ncol = length(bed_list_standard))
# Fill it in
for (i in 1:length(bed_list_standard)) {
  for (j in 1:length(bed_list_standard)) {
    # If diagonal, set to zero
    if (i == j) mtx_to_plot[i, j] <- 0
    # Process only one half, the other is symmetric
    if (i > j) {
      # mtx_to_plot[i, j] <- mtx_to_plot[j, i] <- jaccard(bed_list_standard[[i]], bed_list_standard[[j]])[["jaccard"]]
      mtx_to_plot[i, j] <- mtx_to_plot[j, i] <- GCorr(bed_list_standard[[i]], bed_list_standard[[j]])
    }
  }
}
# Trim row/colnames
rownames(mtx_to_plot) <- colnames(mtx_to_plot) <- str_trunc(names(bed_list_standard), width = 25) 
# Save the plot
# png("man/figures/excluderanges_hg38_jaccard.png", width = 1000, height = 900, res = 200)
if(genome_assembly == "hg38") {
  clust_method <- "euclidean"
}
if(genome_assembly == "mm10") {
  clust_method <- "correlation"
}
pheatmap(data.matrix(mtx_to_plot), cluster_cols = T, cluster_rows = T,
         clustering_method = "ward.D", 
         clustering_distance_rows = clust_method, 
         clustering_distance_cols = clust_method, 
         # annotation_row = mydf, annotation_colors = list(Group = c(PR = mycols[1], CR = mycols[2])),
         treeheight_row = 40,
         treeheight_col = 0, 
         display_numbers = TRUE)
# dev.off()
```

## GenometriCorr

```{r}
# CIS-BP
gr1 <- bed_list_standard[[1]][seqnames(bed_list_standard[[1]]) == "chr1"]
gr2 <- bed_list_standard[[5]][seqnames(bed_list_standard[[5]]) == "chr1"]

# GenometriCorr of smaller query vs. larger reference
# Returns either Jaccard or ECDF area correlation
GCorr <- function(gr1, gr2, return_value = "relative.distances.ecdf.area.correlation") {
  # Select smaller query and larger reference
  if (length(gr1) >= length(gr2)) {
    reference <- gr1
    query <- gr2
  } else {
    reference <- gr2
    query <- gr1
  }
  # GenometriCorr itselv
  gr1_vs_gr2 <- GenometriCorrelation(query, reference, awhole.only = TRUE, showProgressBar = FALSE, permut.number = 0)
  # What to return
  if (return_value == "relative.distances.ecdf.area.correlation") {
    return(gr1_vs_gr2$awhole$relative.distances.ecdf.area.correlation)
  }
  if (return_value == "jaccard.measure") {
    return(gr1_vs_gr2$awhole$jaccard.measure)
  }
}

```
